Rectangulotopes

### 2024-04-22 draft/rectangulotopes.tex
remove example environements

\begin{example}
The weak rectangulotope~$\WRP(4)$ is illustrated in \cref{fig:weakRectangulotope}.
The coordinates of the vertices corresponding to all weak rectangulations are gathered in \cref{tab:verticesWeakRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsWeakRectangulotope}.

@@

\begin{table}
	\centerline{
	\begin{tabular}{c|cccccccccccccc}
		$J$ &
		$1$ &
		$2$ &
		$3$ &
		$4$ &
		$12$ &
		$13$ &
		$14$ &
		$23$ &
		$24$ &
		$34$ &
		$123$ &
		$124$ &
		$134$ &
		$234$
		\\
		\hline
		$f_{\weakeq}(J)$ &
		$3$ &
		$5$ &
		$5$ &
		$3$ &
		$4$ &
		$6$ &
		$5$ &
		$5$ &
		$6$ &
		$4$ &
		$3$ &
		$5$ &
		$5$ &
		$3$
	\end{tabular}
	}
	\caption{The facets of the weak rectangulotope~$\WRP(4)$ of \cref{fig:weakRectangulotope}.}
	\label{tab:facetsWeakRectangulotope}
\end{table}
\end{example}

\begin{comment}
\begin{example}
  The vertex of~$\WRP (16)$ corresponding to the weak rectangulation of \cref{fig:weakRectangulation} is
  \[
  (-3, 0, 26, 2, -9, 5, -69, -4, 17, 0, -8, 59, 2, -20, 0, 2).
  \]
  For instance, the $4$th coordinate is $h^T_4 \cdot v^T_4 - h^S_4 \cdot v^S_4 = 1 \cdot 5 - 1 \cdot 3 = 2$.
  The facet of~$\WRP (16)$ corresponding to the subset~$\{3,4,7,8,9,10,14\}$ is given by the inequality
  \[
  x_3 + x_4 + x_7 + x_8 + x_9 + x_{10} + x_{14} \le ???
  \]
  \vincent{Compute and check...}
\end{example}
\end{comment}

@@

\begin{example}
The strong rectangulotope~$\SRP(4)$ is illustrated in \cref{fig:strongRectangulotope}.
The coordinates of the vertices corresponding to all strong rectangulations are gathered in \cref{tab:verticesStrongRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsStrongRectangulotope}.

@@

\begin{table}
	\centerline{
	\begin{tabular}{c|cccccccccccccc}
		$J$ &
		$1$ &
		$2$ &
		$3$ &
		$4$ &
		$12$ &
		$13$ &
		$14$ &
		$23$ &
		$24$ &
		$34$ &
		$123$ &
		$124$ &
		$134$ &
		$234$
		\\
		\hline
		$f_{\strongeq}(J)$ &
		$6$ &
		$9$ &
		$9$ &
		$6$ &
		$8$ &
		$11$ &
		$10$ &
		$10$ &
		$11$ &
		$8$ &
		$6$ &
		$9$ &
		$9$ &
		$6$
	\end{tabular}
	}
	\caption{The facets of the strong rectangulotope~$\SRP(4)$ of \cref{fig:strongRectangulotope}.}
	\label{tab:facetsStrongRectangulotope}
\end{table}
\end{example}

>>>>

%\begin{example}
For instance, the weak rectangulotope~$\WRP(4)$ is illustrated in \cref{fig:weakRectangulotope}.
The coordinates of the vertices corresponding to all weak rectangulations are gathered in \cref{tab:verticesWeakRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsWeakRectangulotope}.

@@

\begin{table}
	\centerline{
	\begin{tabular}{c|cccccccccccccc}
		$J$ &
		$1$ &
		$2$ &
		$3$ &
		$4$ &
		$12$ &
		$13$ &
		$14$ &
		$23$ &
		$24$ &
		$34$ &
		$123$ &
		$124$ &
		$134$ &
		$234$
		\\
		\hline
		$f_{\weakeq}(J)$ &
		$3$ &
		$5$ &
		$5$ &
		$3$ &
		$4$ &
		$6$ &
		$5$ &
		$5$ &
		$6$ &
		$4$ &
		$3$ &
		$5$ &
		$5$ &
		$3$
	\end{tabular}
	}
	\caption{The facets of the weak rectangulotope~$\WRP(4)$ of \cref{fig:weakRectangulotope}.}
	\label{tab:facetsWeakRectangulotope}
\end{table}
%\end{example}

\begin{comment}
\begin{example}
  The vertex of~$\WRP (16)$ corresponding to the weak rectangulation of \cref{fig:weakRectangulation} is
  \[
  (-3, 0, 26, 2, -9, 5, -69, -4, 17, 0, -8, 59, 2, -20, 0, 2).
  \]
  For instance, the $4$th coordinate is $h^T_4 \cdot v^T_4 - h^S_4 \cdot v^S_4 = 1 \cdot 5 - 1 \cdot 3 = 2$.
  The facet of~$\WRP (16)$ corresponding to the subset~$\{3,4,7,8,9,10,14\}$ is given by the inequality
  \[
  x_3 + x_4 + x_7 + x_8 + x_9 + x_{10} + x_{14} \le ???
  \]
  \vincent{Compute and check...}
\end{example}
\end{comment}
\vincent{not sure if we want to reintroduce this example.}

@@

%\begin{example}
For instance, the strong rectangulotope~$\SRP(4)$ is illustrated in \cref{fig:strongRectangulotope}.
The coordinates of the vertices corresponding to all strong rectangulations are gathered in \cref{tab:verticesStrongRectangulotope}.
The facet inequalities corresponding to each nonempty proper subset of~$[n]$ are gathered in \cref{tab:facetsStrongRectangulotope}.

@@

\begin{table}
	\centerline{
	\begin{tabular}{c|cccccccccccccc}
		$J$ &
		$1$ &
		$2$ &
		$3$ &
		$4$ &
		$12$ &
		$13$ &
		$14$ &
		$23$ &
		$24$ &
		$34$ &
		$123$ &
		$124$ &
		$134$ &
		$234$
		\\
		\hline
		$f_{\strongeq}(J)$ &
		$6$ &
		$9$ &
		$9$ &
		$6$ &
		$8$ &
		$11$ &
		$10$ &
		$10$ &
		$11$ &
		$8$ &
		$6$ &
		$9$ &
		$9$ &
		$6$
	\end{tabular}
	}
	\caption{The facets of the strong rectangulotope~$\SRP(4)$ of \cref{fig:strongRectangulotope}.}
	\label{tab:facetsStrongRectangulotope}
\end{table}
%\end{example}
